**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Acknowledge those that provided feedback on the preprint

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript. This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933). I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases. The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`). Within R I utilized the cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages. A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.

>>>>

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript and to the numerous individuals who provided feedback on the preprint version of the manuscript. This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933). I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases. The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`). Within R I utilized the cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages. A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
